---
title: "20230429_co_occurence_network_NetCoMi_speiceasi_r0.1_clam"
author: "Wu"
date: "2023-04-29"
output: html_document
---
# Load libraries
```{R}

library(SpiecEasi)
library(microbiome)
library(NetCoMi)
library(limma)
library(psadd)
library(data.table)
library(dplyr)
#library(microViz)
library(openxlsx)
library(xlsx)
```


# Read phyloseq data 
```{r}
# bacteria phyloseq object
physeq.Bac<-readRDS("C:/Users/Amanda/Desktop/jobs/Stanford/Mimulus_microbes/Wu_mimulus_analysis2022/02_Analysis/dada2/dada2_B16S/unpooled/phyloseq.rds")
# physeq.Bac<-readRDS("/home/groups/fukamit/ytwu/Wu_mimulus_analysis2022/02_Analysis/dada2/dada2_B16S/unpooled/phyloseq.rds")
physeq.Bac<-prune_samples(sample_sums(physeq.Bac)>=1, physeq.Bac) # prune samples with no reads

# fungi phyloseq object
physeq.Fun<-readRDS("C:/Users/Amanda/Desktop/jobs/Stanford/Mimulus_microbes/Wu_mimulus_analysis2022/02_Analysis/dada2/dada2_ITS1/unpooled_CONSTAX/phyloseq.rds")
physeq.Fun<-prune_samples(sample_sums(physeq.Fun)>=1, physeq.Fun) # prune samples with no reads

# raw counts of bac + fun combined 
physeq.bac.fun<-readRDS( "C:/Users/Amanda/Desktop/jobs/Stanford/Mimulus_microbes/Wu_mimulus_analysis2022/02_Analysis/make_phyloseq_objects/phyloseq.bac.fun_rawcounts.rds")

# make a new column in meta data to combine microbial_community and biotic_inter
table(physeq.bac.fun@sam_data$biotic_inter)
#  No Yes 
# 1030  32 
# examine if biotic_inter = Yes also means fungi_dominated
physeq.bac.fun@sam_data$microbial_community[which(physeq.bac.fun@sam_data$biotic_inter=="Yes")] # no
# exclude the three samples that are not fungi dominated 
biotic_inter.index<-which(physeq.bac.fun@sam_data$biotic_inter=="Yes" & physeq.bac.fun@sam_data$microbial_community== "Fungi_dominated") 
physeq.bac.fun@sam_data$microbial_community_biotic_inter<-physeq.bac.fun@sam_data$microbial_community
physeq.bac.fun@sam_data$microbial_community_biotic_inter[biotic_inter.index]<-"Fungi_domin_long"
physeq.bac.fun@sam_data$microbial_community_biotic_inter<-as.factor(physeq.bac.fun@sam_data$microbial_community_biotic_inter)

physeq.bac.fun@sam_data$microbial_community_biotic_inter<-factor(physeq.bac.fun@sam_data$microbial_community_biotic_inter,
                levels = c("Too_rare", "Co_dominated", "Bacteria_dominated", "Fungi_dominated", "Fungi_domin_long"))

table(physeq.bac.fun@sam_data$microbial_community_biotic_inter)
#           Too_rare       Co_dominated Bacteria_dominated    Fungi_dominated   Fungi_domin_long 
#                518                 48                169                298                 29 

table(physeq.bac.fun@sam_data$microbial_community)
#Bacteria_dominated       Co_dominated    Fungi_dominated           Too_rare 
#               169                 48                327                518 
               
# saveRDS(physeq.bac.fun, "C:/Users/Amanda/Desktop/jobs/Stanford/Mimulus_microbes/Wu_mimulus_analysis2022/02_Analysis/make_phyloseq_objects/phyloseq.bac.fun_rawcounts.rds")
```

# Fungi co-occurrence network 
## spieceasi_fungi_ASV level 
```{r}
physeq.Fun_fun.domin <- subset_samples_no_zero(physeq.Fun, microbial_community== "Fungi_dominated")
physeq.Fun_bac.domin <- subset_samples_no_zero(physeq.Fun, microbial_community== "Bacteria_dominated")


# 25% quantile of sample total reads
quantile(colSums(physeq.Fun@otu_table),0.25) # 352 

# construct network
net_spieceasi.Fun.ASV<- netConstruct(physeq.Fun,
                           filtTax = "highestFreq",
                           filtTaxPar = list(highestFreq = 300),
                           filtSamp = "totalReads",
                           filtSampPar = list(totalReads = 352),
                           measure = "spieceasi",
                           normMethod = "none",
                           #zeroMethod = "pseudoZO",
                           #sparsMethod = "threshold",
                           thresh = 0.1,
                           verbose = 3,
                           dissFunc = "signed",
                            measurePar = list(method = "mb",  pulsar.params = list(rep.num = 10),  symBetaMode = "ave"),
                           seed = 123456)
                           
                           
# network analyzed
props_net_spieceasi.Fun.ASV <- netAnalyze(net_spieceasi.Fun.ASV, clustMethod = "cluster_fast_greedy")

# Plot 
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Fun.ASV.pdf",  width = 8, height = 8)
plot(props_net_spieceasi.Fun.ASV, 
     nodeColor = "cluster", 
     nodeSize = "clr",
     title1 = "Network on ASV level with spieceasi correlations", 
     showTitle = TRUE,
    cexTitle = 1,      cexLabels = 3)

legend(0.7, 1.1, cex = 1, title = "estimated correlation:", 
       legend = c("+","-"), lty = 1, lwd = 3, col = c("#009900","red"), 
       bty = "n", horiz = TRUE)

dev.off()
```

## spieceasi_fungi_ASV level_compare_fungi_dominated vs bacteria_dominated
```{r}
# Split the phyloseq object into two groups
physeq.Fun_fun.domin <- subset_samples_no_zero(physeq.Fun, microbial_community== "Fungi_dominated")
                                                   
net_spieceasi.Fun.ASV.comp<- netConstruct(data=physeq.Fun_fun.domin, 
                                      data2=physeq.Fun_bac.domin, 
                           filtTax = "highestFreq",
                           filtTaxPar = list(highestFreq = 100),
                           filtSamp = "totalReads",
                           filtSampPar = list(totalReads = 352),
                           measure = "spieceasi",
                           normMethod = "none",
                           #zeroMethod = "pseudoZO",
                           #sparsMethod = "threshold",
                           thresh = 0.1,
                           verbose = 3,
                           dissFunc = "signed",
                            measurePar = list(method = "mb",  pulsar.params = list(rep.num = 10),  symBetaMode = "ave"),
                           seed = 123457)

props_net_spieceasi.Fun.ASV.comp <- netAnalyze(net_spieceasi.Fun.ASV.comp, 
                           centrLCC = FALSE,
                           avDissIgnoreInf = TRUE,
                           sPathNorm = FALSE,
                           clustMethod = "cluster_fast_greedy",
                           hubPar = c("degree", "eigenvector"),
                           hubQuant = 0.9,
                           lnormFit = TRUE,
                           normDeg = FALSE,
                           normBetw = FALSE,
                           normClose = FALSE,
                           normEigen = FALSE)

summary(props_net_spieceasi.Fun.ASV.comp)$glob_probs


comp_net_spieceasi.Fun.ASV.comp <- netCompare(props_net_spieceasi.Fun.ASV.comp, 
                          verbose = FALSE,
                          seed = 123456, permTest = TRUE, nPerm = 500)

comp_net_spieceasi.Fun.ASV.comp.sum<-summary(comp_net_spieceasi.Fun.ASV.comp, 
        groupNames = c("Fungi dominated", "Bacteria dominated"),
        showCentr = c("degree", "between", "closeness"), 
        numbNodes = 5)

write.csv(comp_net_spieceasi.Fun.ASV.comp.sum$propdiffs, "/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Fun.ASV.comp.r0.1.sum.csv")

# Plot threshold r > 0.1
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Fun.ASV.comp.r0.1.pdf",  width = 15, height = 8)

plot(props_net_spieceasi.Fun.ASV.comp, 
     sameLayout = TRUE, 
     nodeColor = "cluster",
     nodeSize = "clr",
     groupNames = c("Fungi-dominated", "Bacteria-dominated"),
     showTitle = TRUE,
     sameColThresh = 2,
     cexTitle = 1,cexLabels = 3)

dev.off()


# Plot threshold r > 0.2
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Fun.ASV.comp.r0.2.pdf",  width = 15, height = 8)

plot(props_net_spieceasi.Fun.ASV.comp, 
     sameLayout = TRUE, 
     nodeColor = "cluster",
     nodeSize = "clr",
     edgeFilter  = "threshold",
     edgeFilterPar  = 0.2,
     groupNames = c( "Fungi-dominated", "Bacteria-dominated"),
     showTitle = TRUE,
     sameColThresh = 2,
     cexTitle = 1,cexLabels = 3)

dev.off()

# Plot threshold r > 0.3
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Fun.ASV.comp.r0.3.pdf",  width = 15, height = 8)

plot(props_net_spieceasi.Fun.ASV.comp, 
     sameLayout = TRUE, 
     nodeColor = "cluster",
     nodeSize = "clr",
     edgeFilter  = "threshold",
     edgeFilterPar  = 0.3,
     groupNames = c("Fungi-dominated", "Bacteria-dominated"),
     showTitle = TRUE,
     sameColThresh = 2,
     cexTitle = 1,cexLabels = 3)

dev.off()
```

## spieceasi_fungi_ASV level_compare_within site vs all sites
```{r}
# Split the phyloseq object into two groups -- site specific vs. all sites

site_abb<-unique(physeq.Fun_fun.domin2@sam_data$site_ID)

net_spieceasi.Fun.ASV.comp.site<-list()
props_net_spieceasi.Fun.ASV.comp.site<-list()
comp_net_spieceasi.Fun.ASV.comp.site <-list()
comp_net_spieceasi.Fun.ASV.comp.sum.site<-list()

for(i in 1:length(site_abb)){
  
physeq.Fun_fun.domin2.site<-subset_samples_no_zero(physeq.Fun_fun.domin2, site_ID==site_abb[i])

net_spieceasi.Fun.ASV.comp.site[[i]]<- netConstruct(data=physeq.Fun_fun.domin2.site, 
                                      data2=physeq.Fun_fun.domin2, 
                           filtTax = "highestFreq",
                           filtTaxPar = list(highestFreq = 100),
                           filtSamp = "totalReads",
                           filtSampPar = list(totalReads = 50),
                           measure = "spieceasi",
                           normMethod = "none",
                           #zeroMethod = "pseudoZO",
                           #sparsMethod = "threshold",
                           thresh = 0.1,
                           verbose = 3,
                           dissFunc = "signed",
                            measurePar = list(method = "mb",  pulsar.params = list(rep.num = 10),  symBetaMode = "ave"),
                           seed = 123457)

props_net_spieceasi.Fun.ASV.comp.site[[i]] <- netAnalyze(net_spieceasi.Fun.ASV.comp.site[[i]], 
                           centrLCC = FALSE,
                           avDissIgnoreInf = TRUE,
                           sPathNorm = FALSE,
                           clustMethod = "cluster_fast_greedy",
                           hubPar = c("degree", "eigenvector"),
                           hubQuant = 0.9,
                           lnormFit = TRUE,
                           normDeg = FALSE,
                           normBetw = FALSE,
                           normClose = FALSE,
                           normEigen = FALSE)


comp_net_spieceasi.Fun.ASV.comp.site[[i]] <- netCompare(props_net_spieceasi.Fun.ASV.comp.site[[i]], 
                          verbose = FALSE,
                          seed = 123456, permTest = TRUE, nPerm = 500)

comp_net_spieceasi.Fun.ASV.comp.sum.site[[i]]<-summary(comp_net_spieceasi.Fun.ASV.comp.site[[i]], 
        groupNames = c(paste("Within site", site_abb[i]), "All sites"),
        showCentr = c("degree", "between", "closeness"), 
        numbNodes = 5)
}

site.list.propdiffs<-list()
 site.list.jaccmat<-list()
for(i in 1:length(site_abb)){
  site.list.propdiffs[[i]]<-comp_net_spieceasi.Fun.ASV.comp.sum.site[[i]]$propdiffs
  site.list.jaccmat[[i]]<-comp_net_spieceasi.Fun.ASV.comp.sum.site[[i]]$jaccmat
}
  
# save data frames as different sheets
 # network property 
for(i in c(1:12)){write.xlsx(x =site.list.propdiffs[[i]], 
             file = "/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Fun.ASV.comp_site.propdiff.r0.1.xlsx", 
             sheetName = site_abb[i], append = TRUE)
 }
 
# network similarity based on jaccard index 
 for(i in c(1:12)){write.xlsx(x =site.list.jaccmat[[i]], 
             file = "/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Fun.ASV.comp_site.jaccmat.r0.1.xlsx", 
             sheetName = site_abb[i], append = TRUE)
 }

# Plot an example of the site
site_chosen<-"SB"

pdf(paste0("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Fun.ASV.comp_site", site_chosen, ".r0.1.pdf"),width = 15, height = 8)

plot(props_net_spieceasi.Fun.ASV.comp.site[[9]], 
     sameLayout = TRUE, 
     nodeColor = "cluster",
     nodeSize = "clr",
     edgeFilter = "threshold",
     edgeFilterPar = 0.1,
     groupNames =c(paste("Within site", site_chosen), "All sites"),
     title1 = "Network on ASV level with spieceasi correlations", 
     showTitle = TRUE,
     sameColThresh = 2,
     cexTitle = 1,cexLabels = 3)

dev.off()
```

# Bacteria co-occurrence network
## bacteria-spieceasi correlation
## spieceasi_bacteria_ASV level
```{r}
# 25% quantile of bacteria reads in samples
quantile(colSums(physeq.Bac@otu_table),0.25)

# construct network
net_spieceasi.Bac.ASV<- netConstruct(physeq.Bac,
                           filtTax = "highestFreq",
                           filtTaxPar = list(highestFreq = 300),
                           filtSamp = "totalReads",
                           filtSampPar = list(totalReads = 298),
                           measure = "spieceasi",
                           normMethod = "none",
                           #zeroMethod = "pseudoZO",
                           #sparsMethod = "threshold",
                           thresh = 0.1,
                           verbose = 3,
                           dissFunc = "signed",
                            measurePar = list(method = "mb",  pulsar.params = list(rep.num = 10),  symBetaMode = "ave"),
                           seed = 123456)
                           
                           
# network analyzed
props_net_spieceasi.Bac.ASV <- netAnalyze(net_spieceasi.Bac.ASV, clustMethod = "cluster_fast_greedy")

# Plot 
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Bac.ASV.pdf",  width = 8, height = 8)
plot(props_net_spieceasi.Bac.ASV, 
     nodeColor = "cluster", 
     nodeSize = "clr",
     title1 = "Network on ASV level with spieceasi correlations", 
     showTitle = TRUE,
    cexTitle = 1,      cexLabels = 3)

legend(0.7, 1.1, cex = 1, title = "estimated correlation:", 
       legend = c("+","-"), lty = 1, lwd = 3, col = c("#009900","red"), 
       bty = "n", horiz = TRUE)

dev.off()
```


## spieceasi_bacteria_ASV level_compare_fungi_vs_bacteria_dominated
```{r}
# Split the phyloseq object into two groups
physeq.Bac_fun.domin <- subset_samples_no_zero(physeq.Bac, microbial_community== "Fungi_dominated")
physeq.Bac_bac.domin <- subset_samples_no_zero(physeq.Bac, microbial_community== "Bacteria_dominated")
                                                   
net_spieceasi.Bac.ASV.comp<- netConstruct(data=physeq.Bac_fun.domin, 
                                      data2=physeq.Bac_bac.domin, 
                           filtTax = "highestFreq",
                           filtTaxPar = list(highestFreq = 100),
                           filtSamp = "totalReads",
                           filtSampPar = list(totalReads = 298),
                           measure = "spieceasi",
                           normMethod = "none",
                           #zeroMethod = "pseudoZO",
                           #sparsMethod = "threshold",
                           thresh = 0.1,
                           verbose = 3,
                           dissFunc = "signed",
                            measurePar = list(method = "mb",  pulsar.params = list(rep.num = 10),  symBetaMode = "ave"),
                           seed = 123457)

props_net_spieceasi.Bac.ASV.comp <- netAnalyze(net_spieceasi.Bac.ASV.comp, 
                           centrLCC = FALSE,
                           avDissIgnoreInf = TRUE,
                           sPathNorm = FALSE,
                           clustMethod = "cluster_fast_greedy",
                           hubPar = c("degree", "eigenvector"),
                           hubQuant = 0.9,
                           lnormFit = TRUE,
                           normDeg = FALSE,
                           normBetw = FALSE,
                           normClose = FALSE,
                           normEigen = FALSE)

summary(props_net_spieceasi.Bac.ASV.comp)$glob_probs


comp_net_spieceasi.Bac.ASV.comp <- netCompare(props_net_spieceasi.Bac.ASV.comp, 
                          permTest = TRUE, nPerm = 500,
                          verbose = FALSE,
                          seed = 123456)

comp_net_spieceasi.Bac.ASV.comp.sum<-summary(comp_net_spieceasi.Bac.ASV.comp, 
        groupNames = c("Fungi dominated", "Bacteria dominated"),
        showCentr = c("degree", "between", "closeness"), 
        numbNodes = 5)

write.csv(comp_net_spieceasi.Bac.ASV.comp.sum$propdiffs_lcc, "/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Bac.ASV.comp.r0.1.sum.csv")


# Plot threshold r > 0.1
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Bac.ASV.comp.r0.1.pdf",  width = 15, height = 8)

plot(props_net_spieceasi.Bac.ASV.comp, 
     sameLayout = TRUE, 
     nodeColor = "cluster",
     nodeSize = "clr",
     groupNames = c("Fungi-dominated", "Bacteria-dominated"),
     showTitle = TRUE,
     sameColThresh = 2,
     cexTitle = 1,cexLabels = 3)

dev.off()


# Plot threshold r > 0.2
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Bac.ASV.comp.r0.2.pdf",  width = 15, height = 8)

plot(props_net_spieceasi.Bac.ASV.comp, 
     sameLayout = TRUE, 
     nodeColor = "cluster",
     nodeSize = "clr",
     groupNames = c("Fungi-dominated", "Bacteria-dominated"),
     showTitle = TRUE,
     sameColThresh = 2,
     edgeFilter = "threshold",
     edgeFilterPar = 0.2,
     cexTitle = 1,cexLabels = 3)

dev.off()

# Plot threshold r > 0.3
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Bac.ASV.comp.r0.3.pdf",  width = 15, height = 8)

plot(props_net_spieceasi.Bac.ASV.comp, 
     sameLayout = TRUE, 
     nodeColor = "cluster",
     nodeSize = "clr",
     groupNames = c("Fungi-dominated", "Bacteria-dominated"),
     showTitle = TRUE,
     sameColThresh = 2,
     edgeFilter = "threshold",
     edgeFilterPar = 0.3,
     cexTitle = 1,cexLabels = 3)

dev.off()
```


## spieceasi_bacteria_ASV level_compare_within site vs all sites
```{r}
# Split the phyloseq object into two groups -- site specific vs. all sites

site_abb<-unique(physeq.Bac_bac.domin2@sam_data$site_ID)

net_spieceasi.Bac.ASV.comp.site<-list()
props_net_spieceasi.Bac.ASV.comp.site<-list()
comp_net_spieceasi.Bac.ASV.comp.site <-list()
comp_net_spieceasi.Bac.ASV.comp.sum.site<-list()

for(i in c(1:9,11:12)){ # here I skipped site 10, because for some reason, it has been generating errors at site 10
  
physeq.Bac_bac.domin2.site<-subset_samples_no_zero(physeq.Bac_bac.domin2, site_ID==site_abb[i])

net_spieceasi.Bac.ASV.comp.site[[i]]<- netConstruct(data=physeq.Bac_bac.domin2.site, 
                                      data2=physeq.Bac_bac.domin2, 
                           filtTax = "highestFreq",
                           filtTaxPar = list(highestFreq = 100),
                           filtSamp = "totalReads",
                           filtSampPar = list(totalReads = 50),
                           measure = "spieceasi",
                           normMethod = "none",
                           #zeroMethod = "pseudoZO",
                           #sparsMethod = "threshold",
                           thresh = 0.1,
                           verbose = 3,
                           dissFunc = "signed",
                            measurePar = list(method = "mb",  pulsar.params = list(rep.num = 10),  symBetaMode = "ave"),
                           seed = 123457)

props_net_spieceasi.Bac.ASV.comp.site[[i]] <- netAnalyze(net_spieceasi.Bac.ASV.comp.site[[i]], 
                           centrLCC = FALSE,
                           avDissIgnoreInf = TRUE,
                           sPathNorm = FALSE,
                           clustMethod = "cluster_fast_greedy",
                           hubPar = c("degree", "eigenvector"),
                           hubQuant = 0.9,
                           lnormFit = TRUE,
                           normDeg = FALSE,
                           normBetw = FALSE,
                           normClose = FALSE,
                           normEigen = FALSE)


comp_net_spieceasi.Bac.ASV.comp.site[[i]] <- netCompare(props_net_spieceasi.Bac.ASV.comp.site[[i]], 
                          verbose = FALSE,
                          seed = 123456, permTest = TRUE, nPerm = 500)

comp_net_spieceasi.Bac.ASV.comp.sum.site[[i]]<-summary(comp_net_spieceasi.Bac.ASV.comp.site[[i]], 
        groupNames = c(paste("Within site", site_abb[i]), "All sites"),
        showCentr = c("degree", "between", "closeness"), 
        numbNodes = 5)
}

site.list.propdiffs<-list()
 site.list.jaccmat<-list()
for(i in 1:length(site_abb)){
  site.list.propdiffs[[i]]<-comp_net_spieceasi.Bac.ASV.comp.sum.site[[i]]$propdiffs
  site.list.jaccmat[[i]]<-comp_net_spieceasi.Bac.ASV.comp.sum.site[[i]]$jaccmat
}

# save data frames as different sheets
 # network property 
for(i in c(1:9,11,12)){write.xlsx(x =site.list.propdiffs[[i]], 
             file = "/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Bac.ASV.comp_site.propdiff.r0.1.xlsx", 
             sheetName = site_abb[i], append = TRUE)
 }
 
# network similarity based on jaccard index 
 for(i in c(1:9,11,12)){write.xlsx(x =site.list.jaccmat[[i]], 
             file = "/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Bac.ASV.comp_site.jaccmat.r0.1.xlsx", 
             sheetName = site_abb[i], append = TRUE)
 }

# Plot an example of the site
site_chosen<-"JP"
which(site_abb=="JP") #4

pdf(paste0("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.Bac.ASV.comp_site", site_chosen, ".r0.1.pdf"),width = 15, height = 8)

plot(props_net_spieceasi.Bac.ASV.comp.site[[4]], 
     sameLayout = TRUE, 
     nodeColor = "cluster",
     nodeSize = "clr",
     groupNames =c(paste("Within site", site_chosen), "All sites"),
     title1 = "Network on ASV level with spieceasi correlations", 
     showTitle = TRUE,
     sameColThresh = 2,
     cexTitle = 1,cexLabels = 3)

dev.off()
```

# Fungi Bacteria co-occurrence network
## Fungi Bacteria-spieceasi correlation r = 0.1
## spieceasi_Fungi Bacteria_ASV level
```{r}
# construct network
net_spieceasi.bac.fun.ASV<- netConstruct(physeq.bac.fun,
                           filtTax = "highestFreq",
                           filtTaxPar = list(highestFreq = 100),
                           filtSamp = "totalReads",
                           filtSampPar = list(totalReads = 300),
                           measure = "spieceasi",
                           normMethod = "none",
                           #sparsMethod = "threshold",
                           thresh = 0.1,
                           verbose = 3,
                           dissFunc = "signed",
                            measurePar = list(method = "mb",  pulsar.params = list(rep.num = 10),  symBetaMode = "ave"),
                           seed = 123456)
                           
                           
# network analyzed
props_net_spieceasi.bac.fun.ASV <- netAnalyze(net_spieceasi.bac.fun.ASV, clustMethod = "cluster_fast_greedy")

# Plot 
pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.bac.fun.ASV.r0.1.pdf",  width = 8, height = 8)
plot(props_net_spieceasi.bac.fun.ASV, 
     nodeColor = "cluster", 
     nodeSize = "clr",
     showTitle = TRUE,
    cexTitle = 1,      cexLabels = 3)

legend(0.7, 1.1, cex = 1, title = "estimated correlation:", 
       legend = c("+","-"), lty = 1, lwd = 3, col = c("#009900","red"), 
       bty = "n", horiz = TRUE)

dev.off()

# Plot by Kingdom 

taxtab <- as(tax_table(physeq.bac.fun), "matrix")
Kingdom <- as.factor(taxtab[, "Kingdom"])

# Define Kingdom colors
Kingdomcol <- c("cyan", "deeppink")

pdf("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/net_spieceasi.bac.fun.ASV.r0.1.Kingdom.pdf",  width = 8, height = 8)
plot(props_net_spieceasi.bac.fun.ASV, 
     nodeSize = "clr",
     showTitle = TRUE,
     nodeColor = "feature", 
     featVecCol = Kingdom, 
     colorVec =  Kingdomcol,
    cexTitle = 1,      cexLabels = 3)

legend(0.7, 1.0, cex = 0.6, title = "estimated correlation:", 
       legend = c("+","-"), lty = 1, lwd = 3, col = c("#009900","red"), 
       bty = "n", horiz = TRUE)

dev.off()
```

save.image("/scratch/groups/fukamit/Wu_mimulus_analysis2022/spieceasi_signed_r0.1_clam/spieceasi_signed_r0.1_clam.rdata")

